Lawvere-Tierney Sheafification in Homotopy Type Theory

### 2016-04-07 paper/paper_lipics.tex
minor corrections

In the rest of the section, we suppose given a truncation index
$n\geqslant -1$, and a left exact modality $\modal_n$ on $\Type_n$,
compatible with a left exact modality $\modal_{-1}$ on $\HProp$ in the
sense of condition~\ref{cond:hprop}.

@@

@@

%
This restriction in our formalization may be solved by
generalizing the management of universe polymorphism for recursive definition
%
and by the use of general ``resizing axiom'' which is still under
discussion in the community.
%
We note that for this solution to work, we need to have a more general 
definition of modalities than the one in~\cite{hottlib}, which ask the
reflector $\modal$ to map a universe $\Type^i$ to
itself. Here, we relax this constraint by allowing the reflector to
map a universe $\Type^i$ to a
possibly higher universe $\Type^j$. 
We have checked that the library~\cite{hottlib} still works with this
generalized definition (see
\url{https://github.com/KevinQuirin/HoTT/tree/extended_modalities/} for the
formalization).

>>>>

In the rest of this section, we suppose given a truncation index
$n\geqslant -1$, and a left exact modality $\modal_n$ on $\Type_n$,
compatible with a left exact modality $\modal_{-1}$ on $\HProp$ in the
sense of condition~\ref{cond:hprop}.

@@

\nt{explain why it is acceptable}

@@

%
This restriction in our formalization may be solved by
generalizing the management of universe polymorphism for recursive definition
%
and by the use of general ``resizing axioms'' which are still under
discussion in the community.
%
We note that for this solution to work, we need to have a more general 
definition of modalities than the one in~\cite{hottlib}, which ask the
reflector $\modal$ to map a universe $\Type^i$ to
itself. Here, we relax this constraint by allowing the reflector to
map a universe $\Type^i$ to a
possibly higher universe $\Type^j$. 
We have checked that the library~\cite{hottlib} still works with this
generalized definition after minor modifications (see
\url{https://github.com/KevinQuirin/HoTT/tree/extended_modalities/} for the
formalization).
